\vspace{-\baselineskip} Fast and scalable Gaussian process modeling with applications to astronomical time series \vspace{-2\baselineskip}

### 2017-06-14 paper/ms.tex
section 5 is new
missing caption

\section{Semiseparable matrices \& celerite}\sectlabel{factor}

@@

\begin{figure}[tp]
\begin{center}
\includegraphics[width=\textwidth]{figures/benchmark_darwin.pdf}
\caption{A benchmark showing the computational scaling of \celerite\ using the
    Cholesky factorization routine for rank-$2\,J$ semiseparable matrices as
    described in the text.
    \emph{(left)} The cost of computing \eq{gp-likelihood} with a covariance
    matrix given by \eq{celerite-kernel} as a function of the number of data
    points $N$.
    The different lines show the cost for different numbers of terms $J$
    increasing from bottom to top.
    To guide the eye, the straight black line without points
    shows linear scaling in $N$.
    For comparison, the computational cost for the same model using a general
    Cholesky factorization routine implemented in the Intel MKL linear algebra
    package.
    \emph{(right)} The same information plotted as a function of $J$ for
    different values of $N$.
    Each line shows the scaling for a specific value of $N$ increasing from
    bottom to top.
    The black line shows quadratic scaling in $J$.
    \figurelabel{benchmark}}
\end{center}
\end{figure}

@@

For a similar class of models~--~we return to these below in
\sect{compare}~--~\citet{Kelly:2014} recommend using an ``information
criterion'', such as the Akaike information criterion (AIC) or the Bayesian
information criterion (BIC), as a model selection metric.
These criteria are easy to implement and we use the BIC in \sect{example2}
but, since these are only formally valid under specific sets of assumptions, we
cannot recommend their use in general.

>>>>

\response{
\section{Semiseparable matrices \& celerite}\sectlabel{factor}

@@

\begin{figure}[tp]
\begin{center}
\includegraphics[width=\textwidth]{figures/benchmark_darwin.pdf}
\caption{A benchmark showing the computational scaling of \celerite\ using the
    Cholesky factorization routine for rank-$2\,J$ semiseparable matrices as
    described in the text.
    \emph{(left)} The cost of computing \eq{gp-likelihood} with a covariance
    matrix given by \eq{celerite-kernel} as a function of the number of data
    points $N$.
    The different lines show the cost for different numbers of terms $J$
    increasing from bottom to top.
    To guide the eye, the straight black line without points
    shows linear scaling in $N$.
    For comparison, the computational cost for the same model using a general
    Cholesky factorization routine implemented in the Intel MKL linear algebra
    package is shown as the dashed black line.
    \emph{(right)} The same information plotted as a function of $J$ for
    different values of $N$.
    Each line shows the scaling for a specific value of $N$ increasing from
    bottom to top.
    The black line shows quadratic scaling in $J$.
    \figurelabel{benchmark}}
\end{center}
\end{figure}

@@

For a similar class of models~--~we return to these below in
\sect{compare}~--~\citet{Kelly:2014} recommend using an ``information
criterion'', such as the Akaike information criterion (AIC) or the Bayesian
information criterion (BIC), as a model selection metric.
These criteria are easy to implement and we use the BIC in \sect{example2}
but, since these are only formally valid under specific sets of assumptions, we
cannot recommend their use in general.
}
